Declarative Deployment Reconfiguration of Pulverised Collective Adaptive Systems at Runtime \thanks{ This work has been supported by the Italian PRIN Project COMMON-WEARS (2020HCWWLP) and the EU/MUR FSE REACT-EU PON R\&I 2014-2020. }

### 2023-05-21 paper-2023-acsos-pulverization.tex
Capitalisation of titles @danysk pls check that I also retitled subsections in the eval (btw I also notice that it is not clear what the second scenario is all about... it is quite a generic 'a large-scale scenario where a crowd of people is attending an event in a city

\subsection{Implementation details and underlying runtime}
\label{sec:contrib:runtime}

@@

\subsection{Small scale: crowd alert}
\label{sec:small-scale-crowd-alert}

@@

\subsection{Large scale: urban event}

@@

\subsection{Application description languages: component-based software engineering and the pulverisation model}
\label{sec:rw:whatsw}
%
%% A first distinction revolves around whether 
%% the distributed software to be deployed 
%% is a monolith 
%% or is already broken into different components.
%
We consider a distributed application 
 as a graph of deployable units.
%
This partitioning may be 
 manually specified at development time
 (e.g., by explicitly defining and packaging different components)
 or automatically defined
 through \emph{application partitioning} approaches~\cite{DBLP:journals/jnca/LiuASGBQ15}. %exploiting the natural modularity of code (depending on the paradigm and language adopted).

@@

\subsection{Infrastructure and deployment description languages}
\label{sec:rw:depdesc}

@@

\subsection{Automatic/autonomic deployment and reconfiguration}
\label{sec:rw:autodep}
%
A comprehensive conceptual framework
 on automatic deployment of distributed systems
 is provided in~\cite{DBLP:journals/jss/ArcangeliBL15}.
%
A more recent survey~\cite{coullon2023swreconfig} focuses
 on formal techniques for verifying the correctness of reconfigurations
 in component-based distributed software systems.
%
Two formal models for specifying reconfigurable architectures are
\emph{DR-BIP}~\cite{Ballouli18dr-bip}
and \emph{DReAM}~\cite{denicola2020dream-dynamic-reconfig-arch-modelling}.
%
Both are based on the same conceptual model: they 
 feature \emph{components} (capturing behaviour),
\emph{connectors} (capturing interaction between components' \emph{ports}),
\emph{maps} (logical topologies),
and \emph{deployments} (associating components to map locations),
overall organised in \emph{motifs} (dynamic architectural configurations),
to model and analyse dynamic architectures.
%
%\meta{TODO: say something about our positioning wrt verification of reconfigurations}

>>>>

\subsection{Implementation Details and the Runtime System}
\label{sec:contrib:runtime}

@@

\subsection{Small-Scale Scenario: Crowd Alert in a Lab}
\label{sec:small-scale-crowd-alert}

@@

\subsection{Large-Scale Scenario: Collective Computation at a Urban Event}

@@

\subsection{Application Description Languages: Component-based Software Engineering and the Pulverisation Model}
\label{sec:rw:whatsw}
%
%% A first distinction revolves around whether 
%% the distributed software to be deployed 
%% is a monolith 
%% or is already broken into different components.
%
We consider a distributed application 
 as a graph of deployable units.
%
This partitioning may be 
 manually specified at development time
 (e.g., by explicitly defining and packaging different components)
 or automatically defined
 through \emph{application partitioning} approaches~\cite{DBLP:journals/jnca/LiuASGBQ15}. %exploiting the natural modularity of code (depending on the paradigm and language adopted).

@@

\subsection{Infrastructure and Deployment Description Languages}
\label{sec:rw:depdesc}

@@

\subsection{Automatic/Autonomic Deployment and Reconfiguration}
\label{sec:rw:autodep}
%
A comprehensive conceptual framework
 on automatic deployment of distributed systems
 is provided in~\cite{DBLP:journals/jss/ArcangeliBL15}.
%
A more recent survey~\cite{coullon2023swreconfig} focuses
 on formal techniques for verifying the correctness of reconfigurations
 in component-based distributed software systems.
%
Two formal models for specifying reconfigurable architectures are
\emph{DR-BIP}~\cite{Ballouli18dr-bip}
and \emph{DReAM}~\cite{denicola2020dream-dynamic-reconfig-arch-modelling}.
%
Both are based on the same conceptual model: they 
 feature \emph{components} (capturing behaviour),
\emph{connectors} (capturing interaction between components' \emph{ports}),
\emph{maps} (logical topologies),
and \emph{deployments} (associating components to map locations),
overall organised in \emph{motifs} (dynamic architectural configurations),
to model and analyse dynamic architectures.
%
%\meta{TODO: say something about our positioning wrt verification of reconfigurations}
